Clearance Project - 3 - TKstats

### 2025-03-19 data-raw/ClearanceProject-3-TKstats.Rmd
Merge feature/Rclearance_comparison to dev (#22)
* Added diff_log_cvt() call for oral and iv.

* Changed log_likelihood() to work with pre-calculated predictions from other sources. Still requires sigma.

* Quick fix to get_fit.pk which no longer needs unnesting.

* Renamed and initialized 4 analysis documents for clearance project.

* Added data associated with clearance project for efficient loading.

* Organized ongoing hepatic clearance project files in data-raw/

```{r data-loading}
# Note that you should run ...-1-Data.Rmd before this
# RCdata/ is a directory that is not tracked by git because it contains
# large files 
this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
load("data-raw/RCdata/chem_lists.RData")
load("data-raw/plasma_CvTfits_data.RData")
load("data-raw/RCdata/rat_pars_human.RData")
load("data-raw/RCdata/rat_pars_rat.RData")
all_chem_properties <- readRDS("data-raw/RCdata/ctxR_3comp2_cheminfo.rds")
full_pk <- readRDS("data-raw/all_cvt_pk.rds")
full_tkstats <- get_tkstats(full_pk)
```

>>>>

```{r data-loading}
# Note that you should run ...-1-Data.Rmd before this
# RCdata/ is a directory that is not tracked by git because it contains
# large files 
this_pk <- readRDS("data-raw/plasma_CvTfits.rds")
load("data-raw/chem_lists.RData")
load("data-raw/plasma_CvTfits_data.RData")
load("data-raw/rat_pars_human.RData")
load("data-raw/rat_pars_rat.RData")
all_chem_properties <- readRDS("data-raw/RCdata/ctxR_3comp2_cheminfo.rds")
full_pk <- readRDS("data-raw/all_cvt_pk.rds")
full_tkstats <- get_tkstats(full_pk)
```
